Supporting Information for "Ship-based lidar evaluation of Southern Ocean low clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses"

### 2025-07-21 si_rev1.tex
Fix grammar

\begin{figure}[p!]
\includegraphics[width=\textwidth]{img/stats_hist_si.pdf}
\caption{
Histograms and averages of \textbf{(a, c)} liquid water path, and \textbf{(b, d)} ice water path in CERES SYN1deg observations (OBS), ICON,
MERRA-2, and ERA5 for \textbf{(a, b)} all and \textbf{(c, d)} cloudy profiles. All campaigns are weighted equally. The statistics are calculated from daily mean values corresponding to each time step and geographical location of the voyage tracks and stations.
}
\label{fig:stats-hist-si}
\end{figure}

>>>>

\begin{figure}[p!]
\includegraphics[width=\textwidth]{img/stats_hist_si.pdf}
\caption{
Histograms and averages of \textbf{(a, c)} liquid water path and \textbf{(b, d)} ice water path in CERES SYN1deg observations (OBS), ICON, MERRA-2, and ERA5 for \textbf{(a, b)} all and \textbf{(c, d)} cloudy profiles. All campaigns are weighted equally. The statistics are calculated from daily mean values corresponding to each time step and geographical location of the voyage tracks and stations.
}
\label{fig:stats-hist-si}
\end{figure}
